\documentclass[11pt]{article}

\begin{document}

\title{Tutorial 1 Report}
\author{M Shepherd, 19059019; M von Fintel, 20058837}
\date{8 August 2018}

\maketitle

\section{Project Description}

This project was to implement a single server, multiple client chat program.
Many clients can connect to the server and can chat, that being send messages to
all the other clients connected to the server. Clients can also send messagest to
other individual clients in a function known as Whispering. What follows is a brief,
consise description of the different parts of the project.

\subsection{The Server}

The server handles all the incoming messages sent from clients and sends them on
to all the other clients. It creates a ServerSocket on port 8000. It continually
listens for new clients to connect and creates a new socket each time someone
does. It is therefore a multi-threaded implementation. More will be said on this
when the client side is discussed.
\\\\
There is currently a limit to the amount of clients that
can join to make sure cleints have a seamless exclusive experience. This is currently set
at ten clients. If the chatroom is full, i.e. there are already ten clients, the new client
will be warned with an appropriate message and will be shutdown.

\subsection{The Client}

The client runs behind a GUI. The GUI has text areas for the chat and message
composing. A list of online users is also displayed. When the user starts the
client, the client connects to the server, the user has to input a username and the host (IP
address of the server) they wish to connect to. The input is done via JOption.showInputDialog().
The inputted host is verified and the user is notified if it is unknown. If it is known, the client
connects to the Server at that host. The username is also checked agains the list of online users to
make sure it will be unique.
\\\\
The client then listens for messages that come in the DataInputStream from the Server.
All messages, including whispers, and the list of online users are sent to clients on
this DataInputStream. Messages types are identified by the prefix of the string. For
example, if the message starts with "*userNames*", then it is a string representation
of the list of online users.
\\\\
Sending messages, whispering etc are all done by buttons that have ActionPerformed
listeners. 

\section{Features}

\subsection{Included Features}

\subsection{Not Included Features}

\subsection{Extra Features}

\section{Algorithms and Data Structures Used}

\end{document}
